Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-07-16 latex/tex/experiments.tex
added texshop hooks and references

	Given its size, \image{} can only scale from $10$ Summit nodes.
	\item \textit{Synthetic Dataset}:
	Our synthetic dataset is the same shape of \image{} but consists of fewer rows and columns by a factor of $3$. The resulting matrix is $1048576 \times 11042$. 
	We chose a smaller size dataset to better see the limits of scaling and to scale from fewer Summit nodes.
\end{itemize}

>>>>

	Given its size, \image{} can only scale from $10$ Summit nodes.
	\item \textit{Synthetic Dataset}:
	Our synthetic dataset has the same aspect ratio of \image{} but consists of fewer rows and columns by a factor of $3$. The resulting matrix is $1048576 \times 11042$. 
	We chose a smaller size dataset to fit on a single node.
\end{itemize}

### 2020-07-16 latex/tex/prelims.tex
added texshop hooks and references

Scaling algorithms for NMF to large data often requires parallelization in order to fit the data across the memories of multiple compute nodes or speed up the computation to complete in reasonable time.
Parallelizations of multiple optimization approaches have been proposed for general NMF. \GB{add more citations here, including to SmallK}
In particular, we build upon the work of Kannan et al. \cite{KBP16,KBP17,EH+19-TR} and the open-source library PLANC, designed for nonnegative matrix and tensor factorizations of dense and sparse data.
In this parallelization, the alternating optimization approach is employed with various options for the algorithm used to (approximately) solve the NNLS subproblems.
The efficiency of the parallelization is based on scalable algorithms for the parallel matrix multiplications involved in all NNLS algorithms; these algorithms are based on Cartesian distributions of the input matrix across 1D or 2D processor grids.

>>>>

Scaling algorithms for NMF to large data often requires parallelization in order to fit the data across the memories of multiple compute nodes or speed up the computation to complete in reasonable time.
Parallelizations of multiple optimization approaches have been proposed for general NMF \cite{FKPB15,BW09,MESPS20,KBP17,SmallK}. 
In particular, we build upon the work of Kannan et al. \cite{KBP16,KBP17,EH+19-TR} and the open-source library PLANC, designed for nonnegative matrix and tensor factorizations of dense and sparse data.
In this parallelization, the alternating optimization approach is employed with various options for the algorithm used to (approximately) solve the NNLS subproblems.
The efficiency of the parallelization is based on scalable algorithms for the parallel matrix multiplications involved in all NNLS algorithms; these algorithms are based on Cartesian distributions of the input matrix across 1D or 2D processor grids.
